A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{key_exchange}
    \caption{Encryption key exchange process.}
    \label{fig:key_exchange}
\end{figure}

\subsection{Unsubscribe to Data Products}
Data consumers can unsubscribe to data products when they're not interested anymore. Product Contract marks the consumer as not subscribing, corresponding to the parameter $isSubscribe$ in $Product$ structure, since the delete function in Solidity does not remove the actual element but resetting it to default value. When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers. The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.

In SaaS, the cancellation fee is a way to make sure the service providers are protected. It is commonly used in pre-paid subscription-based services that allows service providers charge cancellation fee if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.

Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data. The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.
\begin{align}
\label{equation:unsubscribe}
    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \\
    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \\
    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
\end{align}
\subsection{Refund}
\label{section:refund}
Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee. Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective. When the refund procedure is launched, all consumers vote to decide whether the refund is established. Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following.

>>>>

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{key_exchange_reorganize}
    \caption{Encryption key exchange process.}
    \label{fig:key_exchange}
\end{figure}

\subsection{Unsubscribe to Data Products}
When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription. In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied. Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data. The new key should be updated for the remaining subscribers.
\begin{align}
    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
\end{align}
\subsection{Refund}
\label{section:refund}
The refund topics is complicated in a subscription services, therefore, we illustrated the challenges in this section. As the subscription-based services in real world, participants can launch a refund in following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee. However, issues such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully. Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers. If they can't reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product. Third, the refund could launch by providers when they can't maintain products as committed.
